Estimating the magnetization distribution within rectangular rock samples

### 2016-06-17 manuscript/manuscript.tex
improve the decription of the discretization

at an observation point located on the observation plane $\alpha$, 
the $z^{\prime}$-component of the magnetic induction (flux density) 

@@

The measured $z^{\prime}$-component at the point 
$(x^{\prime}, y^{\prime}, z^{\prime})$ on the plane
$\alpha$ (Figure \ref{fig:sample-planes-cross}) can be described as a 

@@

\tilde{d}^{\prime}(x^{\prime}, y^{\prime}, z^{\prime}) = 

@@

w(\eta, \zeta) \; d^{\prime}(x^{\prime} - \eta, 
                             y^{\prime} - \zeta,
                             z^{\prime}) \, d\eta d\zeta \: ,

@@

where $w(\eta, \zeta)$ is the sensor answer function \citep{egli2000}. 

@@

w(x^{\prime}, y^{\prime}) = \begin{cases}

@@

1/A &\: , \quad (x^{\prime}, y^{\prime}) \in A \\
0 &\: , \quad (x^{\prime}, y^{\prime}) \notin A

@@

\tilde{d}^{\prime}(x^{\prime}, y^{\prime}, z^{\prime}) = \frac{1}{A} 

@@

d^{\prime}(x^{\prime} - \eta, y^{\prime} - \zeta, z^{\prime}) \, d\eta d\zeta \: .

@@

$\Delta A$ (Figure \ref{fig:b-mag-flux-approx}b).

@@

\tilde{d}^{\prime}_{i} \approx \frac{\Delta A}{A} \sum \limits_{j = 1}^{Q} d^{\prime}_{j} \: ,

@@

where $\tilde{d}^{\prime}_{i}$ is the measured 
$z^{\prime}$-component at the $i$th observation point
located at the center of the sensor active area $A$
(black circle in Figure \ref{fig:b-mag-flux-approx}b) and 
$d^{\prime}_{j}$ is the $z^{\prime}$-component at the
point $(x^{\prime}_{j}, y^{\prime}_{j})$, $j = 1, ..., Q$

@@

The $\tilde{d}^{\prime}_{i}$ measured on plane $\alpha$
is the $i$th element of the vector $\mathbf{d}^{0}_{z^{\prime}}$
(equation \ref{eq:obs-data-vec-LCS}).
Hence, by substituting $\Delta A = A/Q$ in equation {eq:b-mag-flux-approx}, 
we get
\tilde{d}^{\prime}_{i} \approx \frac{1}{Q} \sum \limits_{j = 1}^{Q} d^{\prime}_{j} \: .
\label{eq:b-mag-flux-approx2}
Equation \ref{eq:b-mag-flux-approx2} shows that the measured
$z^{\prime}$-component $\tilde{d}^{\prime}_{i}$ 
at the $i$th observation point on a plane $\alpha$ is
approximately given by the magnetic induction
averaged over the active area $A$ of the sensor.

@@

 \begin{figure}
 \noindent \includegraphics[width=20pc]{Figs/Fig4b_HQ.pdf}
 \caption{Schematic representation of the integral \ref{eq:Phi-mag-flux2}.
 (a) Magnetic sensor with active area $A$ (light grey square) located at
 a distance $h$ of the sample (grey prism). (b) Detailed representation
 of the sensor active area $A$, which is centered at the observation point
 $(x^{\prime}, y^{\prime})$ (black circle). The square active area is discretized into 
 a regular grid of $Q$ square cells (limited by the dashed lines). Each
 cell is centered at a point $(x^{\prime}_{j}, y^{\prime}_{j})$, 
 $j = 1, ..., Q$, (open circles) and has an area $\Delta A$ equal to $A/Q$.}
 \label{fig:b-mag-flux-approx}
 \end{figure}

>>>>

at the $i$th observation point $(x^{\prime}_{i}, y^{\prime}_{i}, z^{\prime}_{i})$, 
$i = 1, ..., N$, located on an observation plane $\alpha$,
$\alpha = 0, ..., 3$ , the $z^{\prime}$-component of 
the magnetic induction (flux density) 

@@

For convenience, let us denote this observed $z^{\prime}$-component
as $\tilde{d}_{i} \equiv \tilde{d}^{\prime}(x^{\prime}_{i}, y^{\prime}_{i}, z^{\prime}_{i})$,
which represents the $i$th element of a particular vector 
$\mathbf{d}^{\alpha}_{z^{\prime}}$ (equation \ref{eq:obs-data-vec-LCS}),
depending on the observation plane $\alpha$ on 
which the measurement is done.
This observed data $\tilde{d}_{i}$ can then be described as a 

@@

\tilde{d}_{i} = 

@@

w(\eta, \zeta) \; d^{\prime}(x^{\prime}_{i} - \eta, 
                             y^{\prime}_{i} - \zeta,
                             z^{\prime}_{i}) \, d\eta d\zeta \: ,

@@

where $w(\eta, \zeta)$ is the sensor answer function \citep{egli2000}
and $d^{\prime}(x^{\prime}_{i} - \eta, y^{\prime}_{i} - \zeta, z^{\prime}_{i})$
represents the theoretical values of the $z^{\prime}$-component of 
the magnetic induction produced by the rock sample at the points located on 
the observation plane $\alpha$ with constant 
$z^{\prime}_{i}$ (Figure \ref{fig:sample-planes-cross}).

@@

w(x^{\prime}_{i}, y^{\prime}_{i}) = \begin{cases}

@@

1/A &\: , \quad (x^{\prime}_{i}, y^{\prime}_{i}) \in A \\
0 &\: , \quad (x^{\prime}_{i}, y^{\prime}_{i}) \notin A

@@

\tilde{d}^{\prime}_{i} = \frac{1}{A} 

@@

d^{\prime}(x^{\prime}_{i} - \eta, y^{\prime}_{i} - \zeta, z^{\prime}_{i}) \, d\eta d\zeta \: .

@@

$\Delta A = A/Q$ (Figure \ref{fig:b-mag-flux-approx}b).

@@

\tilde{d}^{\prime}_{i} \approx \frac{1}{Q} \sum \limits_{j = 1}^{Q} d^{\prime}_{j} \: ,

@@

where $d^{\prime}_{j}$ is the theoretical value of the 
$z^{\prime}$-component of the magnetic induction produced by the rock
sample at the point $(x^{\prime}_{j}, y^{\prime}_{j})$, $j = 1, ..., Q$

@@

Equation \ref{eq:b-mag-flux-approx} shows that the measured
$z^{\prime}$-component $\tilde{d}^{\prime}_{i}$ is
approximately given by the averaged magnetic induction
produced by the rock sample over the active area $A$ of the sensor.

@@

 \begin{figure}
 \noindent \includegraphics[width=20pc]{Figs/Fig4b_HQ.pdf}
 \caption{Schematic representation of the discretization
 used for approximating the integral \ref{eq:b-mag-flux2} by 
 the summation \ref{eq:b-mag-flux-approx}.
 (a) Magnetic sensor with active area $A$ (light grey square) located at
 a distance $h$ of the sample (grey prisms), on a particular observation
 plane $\alpha$ (Figures \ref{fig:sample-planes} and 
 \ref{fig:sample-planes-cross}). (b) Detailed representation
 of the sensor active area $A$, which is centered at the observation point
 $(x^{\prime}_{i}, y^{\prime}_{i})$ (black circle). The square active area 
 of the sensor is discretized into a regular grid of $Q$ square cells 
 (limited by the dashed lines). Each cell is centered at a point 
 $(x^{\prime}_{j}, y^{\prime}_{j})$, $j = 1, ..., Q$, (open circles) and 
 has an area $\Delta A = A/Q$.}
 \label{fig:b-mag-flux-approx}
 \end{figure}
